Quality Definitions of Qualities

### 2019-12-16 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
update defnitions reliability, installability

\begin{defn}  
  A program is functionally correct if it behaves according to its stated
  functional specifications \citep{GhezziEtAl2003}.  \wss{This is not how
    \citet{GhezziEtAl2003} defines correctness.  They only require satisfaction
    of the functional requirements.} \oo{Updated} \wss{Is this verbatim from the
    original source?  If not, we should show those parts that are verbatim in
    quotes, so that readers know the parts that were developed by us.}

@@

\begin{defn}
  The probability that the software will operate as expected over a specified
  time interval \citep{GhezziEtAl2003}.  \wss{Is this verbatim from
    \citet{GhezziEtAl2003}?}
\end{defn}

@@

\begin{defn} \label{reliabilitySelected2} 
  Reliability expresses the ability of the software to maintain a specified
  level of fault tolerance, when used under specified condition
  \citep{singh2013different}.
\end{defn}

\begin{defn}
  The extent to which a program can be expected to perform its intended function
  with required precision \citep{McCallEtAl1977}. \oo{Check definition with pdf}
\end{defn}

\begin{defn}
  Informally, the reliability of a system is the probability, over a given
  period of time, that the system will correctly deliver services as expected by
  the user \citep{sommerville}
\end{defn}

\begin{defn}
  The ability of a system or component to perform its required function under
  stated conditions for a specified period of time
  \citep{IEEEComputerDictionary1991}
\end{defn}

\wss{Olu, have you looked at the later chapters of the \citet{GhezziEtAl2003}?
  I believe there is a statistical definition of reliability there.}

@@

Definition \ref{reliabilitySelected1} and \ref{reliabilitySelected2} rephrased:
Probability of failure-free operation of a computer program in a specified
environment for a specified time at a specified level of fault tolerance.

@@

Reliability is defined in a way that the measurement metrics are visible - the
specified environment, the specified time and the specified level of fault
tolerance. Reliability is a critical quality for scientific software, since the
results of computations are meaningless, if they are not dependable.
Reliability is closely tied to verifiability, since the key quality to verify is
reliability, while the act of verification itself improves reliability.

Reliability models can be used to predict reliability of a software product. For
example measuring Mean Time to Fail (MTTF) can be a good measure of reliability
\citep{berander2005software}.

>>>>

\begin{defn}  
  A program is functionally correct if it behaves according to its stated
  functional specifications \citep{GhezziEtAl2003}.   \wss{Is this verbatim from the original source?  If not, we should show those parts that are verbatim in
  quotes, so that readers know the parts that were developed by us.}
  \oo{Yes, verbatim}

@@

\begin{defn}
  Informally, software is reliable if the user can depend on it \citep{GhezziEtAl2003}.
\end{defn}

@@

\begin{defn}
  Reliability expresses the ability of the software to maintain a specified
  level of fault tolerance, when used under specified condition
  \citep{singh2013different}.
\end{defn}

\begin{defn}
  Extent to which a program can be expected to perform its intended function
  with required precision \citep{McCallEtAl1977}. \oo{Definition check pass}
\end{defn}

\begin{defn}
  Informally, the reliability of a system is the probability, over a given
  period of time, that the system will correctly deliver services as expected by
  the user \citep{sommerville}.
\end{defn}

\begin{defn}
  The ability of a system or component to perform its required function under
  stated conditions for a specified period of time
  \citep{IEEEComputerDictionary1991}.
\end{defn}

\begin{defn}
  The ability of a system to perform its required functions under stated conditions whenever required—having a long mean time between failures \citep{mcconnell2004code}.
\end{defn}
\begin{defn} \label{reliabilitySelected2} 
	Reliability can be estimated as ``the average time interval between two faliures, also called the mean time to faliure (MTTF). Clearly, MTTF (t) = 1/FI (t)''. Where FI (t) is the faliure intensity - the number of faliures per unit time \citep{GhezziEtAl2003}.
\end{defn}
\oo{Statistical definition from  \citep{GhezziEtAl2003} added}

@@

Definition \ref{reliabilitySelected1} and \ref{reliabilitySelected2} rephrased:
Probability of failure-free operation of a computer program in a specified
environment for a specified time, i.e. the average time interval between two faliures also known as the mean time to failure (MTTF).

@@

Reliability is defined such that the measurement metrics are visible - the
specified environment and time.
